### 2018-11-12 Sabanci_talk/Sabanci_talk.tex
v3 finished

\begin{frame}{Interferometers : \red{Triangular}-topology}{Einstein Telescope}
  \vspace{-2mm}
  Three $60^\circ$ V-IFOs, one redundant (null stream), $\sin 60^\circ =\sqrt{3}/2$.
  \begin{footnotesize}
  \begin{align*}
    &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\hspace{2cm}\\
    & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
    & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
    &  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
    \end{align*}
    \end{footnotesize}
   %
    \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
    \end{tikzpicture}
    %
   \onslide<2->
   {
      No blind spots!
      \begin{footnotesize}
      \begin{align*}
      F^2_\bigtriangleup &\equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 \hspace{8cm}\\ 
      &= \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right)
      \end{align*}
      \end{footnotesize}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]

@@

\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
  \vspace{-5mm}
  \begin{footnotesize} 
  \[
  \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  \]
  \\
  \end{footnotesize}
  $\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
  \\
  \onslide<2->
  {
    \vspace{3mm}
    Recall, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
    \begin{footnotesize} 
    \[
    \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
    \]
    \end{footnotesize}
  }
  %
  \onslide<3->
  RMS \red{average} over the angles 
  \begin{small}
  $ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
  \end{small}
  \begin{footnotesize} 
  \[
  \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
  \]
  \end{footnotesize}
  %
  Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
  \begin{footnotesize} 
  \[
  0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
  \]
  \end{footnotesize}
  % 
\end{frame}

\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
%
  \begin{footnotesize} 
  \begin{align*}
  \rho_{\text{tot},\llcorner} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
  \rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
  \end{align*}
  \end{footnotesize}
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
  \end{tikzpicture}
  \\
  %\vspace{2mm}
  \onslide<2->
  {
    $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
    \begin{footnotesize} 
    \[
    \rho^2_{\text{tot},\bigtriangleup} = \sum_{A=1}^3 \left(\rho^A\right)^2  =  A^2 \rho_c^2 \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
    \]
    \end{footnotesize}
    \\
  }
  \onslide<3->
  Use \bl{RMS-averaged} $|Q|^2$
  \begin{footnotesize}
  \begin{align*}
  \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  &=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
  \end{align*}
  \end{footnotesize}
  \\
  %where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
  \vspace{-5mm}
  Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
  \vspace{10mm}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
  \end{tikzpicture}
  %
  % 
\end{frame}

@@

\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
\vspace{-7mm}
  \begin{footnotesize}
    \begin{align*}
      &\tau_\text{insp}^{0\text{PN}} \ \ \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \ \ \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
    \end{align*}
  \end{footnotesize}
  \onslide<2->
  {
  What about the SNR? \quad
  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
  \end{small}
  }
  %

%
\begin{tikzpicture}[overlay,remember picture]
    \onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
    {\begin{footnotesize} 
      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
    \end{footnotesize}}; 
    \onslide<2->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(4.1cm,0.1cm)}]current page.center) 
    {\begin{footnotesize} 
      $ \tilde{A}_{i=h,m,l}=A\left\{\tfrac{4}{5},  \tfrac{2}{5},   < \tfrac{1}{5}\right\}$    
    \end{footnotesize}};  
    \onslide<3->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.2cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_{i} = \left\{29.2, \ 14.6, \ 6.11 \right\}$    
    \end{footnotesize}}; 
    \onslide<4->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-2.6cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_\text{LHV} = \{ 26.4, 18.8 , 2.0\} $    
    \end{footnotesize}};
    \onslide<3->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
    {\begin{footnotesize} 
      $\rho_\text{tot} = 32.6 $    
    \end{footnotesize}};
    \onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{The era of Einstein Telescope}{BNS detections}
 Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$\\
 \red{Two} ET configurations:\qquad \textcolor{brown}{B} (high $f$), \red{C} (low $f$)
 \begin{tikzpicture}[overlay,remember picture]
      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted_pres.pdf}};
      \onslide<2->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_B_SNR_int.pdf}};
      \onslide<3->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_C_SNR_int.pdf}};
\end{tikzpicture}      
\end{frame}

\begin{frame}{The era of Einstein Telescope}{GRB \red{Forecast} Prospects } 
  \vspace{-8mm}
  \begin{footnotesize}
  \begin{table}[h]
  \centering
  \begin{tabular}{lccccccc}
  %toprule
  \hline\hline
  $D\,$(Mpc) & \multicolumn{3}{c}{ET-B} & $R_\text{av}{}^\text{max}_\text{min} $ & \multicolumn{3}{c}{ET-C}\T\B\\
  \hline
  {}& $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}$ \ \hspace{3mm} & $\bar{\rho}_{F}$ & {}  & $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}\hspace{3mm}$& $\bar{\rho}_{F}$\T\B\\
  %midrule
  100 & $\approx\,$6.72 &  47.0\,minutes & 306 & $ 1.54^{4.7}_{0.3}$ & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
  200 & $\approx\,$11.2 & 11.6\,minutes & 152 &  $ 12.3^{38}_{2.6} $ & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
  400 & $\approx\,$18.2 & 3.00\,minutes & 75.7 &$ 98.6^{300}_{20} $ & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
  600 & $\approx\,$26.0  &65.8\,seconds & 50.2& $ 333^{1020}_{69} $ &    $\approx\,$5.7 & 1.03\,hours & 60.0  \\
  \hline\hline
  %bottomrule
  \end{tabular}
  \caption*{Event rates using $R=1540^{+3200}_{-1220}\,\text{Gpc}^{-3}\,\text{yr}^{-1}$ inferred from GW170817}
  \end{table}
  \end{footnotesize}
  %
  \vspace{-3mm}
  \onslide<2->Very \red{high SNRs} $\Rightarrow \ord(\rho_F^{\red{-1}})$-precision parameter estimation afterward \\
  \vspace{2mm}
  \onslide<3->\bl{ET-B} $\Longrightarrow $ forecasts not likely \\
  \vspace{2mm}
  \onslide<4->\red{ET-C} $\Longrightarrow T_\text{AW} \ge 1\,$hour within 600\,Mpc\\
  \vspace{1mm}
  \textcolor{white}{ET-C} $\Longrightarrow \red{\ord(100)}$ {\bf BNS forecasts} yearly! $\Rightarrow $ 1 per day!\\
  \vspace{1mm}
  \onslide<5->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(10)}$ with \red{3\,hours} of warning \\
  \vspace{1mm}
  \onslide<6->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(2)}$ with \red{5\,hours} of warning
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<3>\node[draw, blue,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (-2.3,5.3){};
      \onslide<4->\node[draw, red,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (3.6,5.3){};
  \end{tikzpicture}
\end{frame}

\begin{frame}{The era of Einstein Telescope}{Source localization before the merger} 
  ET is very sensitive, but all 3 IFOs are at one place. \\
  \vspace{1mm}
  $\Longrightarrow$ \red{poor} sky localization \\
  \vspace{1mm}
  \onslide<2->BUT \ldots \\
  \begin{itemize}
  \item With $T_\text{AW} \sim\,$hours, Earth's rotation matters!
  \item Two hours $\Rightarrow 30^\circ \Rightarrow \approx 2000\,$km of IFO distance $\sim\,$L1-H1 separation
  \end{itemize}
  \onslide<3->So, within 1\,Gpc, ET {\bf alone} will localize
  \begin{itemize}
  \item 20\% of the sources to within 100\,deg$^2$
  \item 2\% to within 20\,deg$^2$
  \item 0.5\% to within 10\,deg$^2$ 
  \onslide<4->\item[]$\Longrightarrow \red{\ord(5)}$ sources within 400\,Mpc
  \end{itemize}
  \onslide<5->10\,deg$^2$: LSST's field of view\\
  \onslide<6-> Numbers improve with \bl{Cosmic Explorer} ($f\gtrsim \red{5}\,$Hz)
  %
  \begin{tikzpicture}[overlay,remember picture]
	\onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.2cm,2.25cm)}]current page.center) {\includegraphics[height=3cm]{figs/Earth_rot.png}};
	\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.3cm,-2.25cm)}]current page.center) {\includegraphics[height=3.9cm]{figs/LSST.jpg}};
  \end{tikzpicture}
\end{frame}

>>>>

\begin{frame}{Interferometers : \red{Triangular}-topology}{Einstein Telescope}
  \vspace{-2mm}
  \bl{Three} $60^\circ$ \red{V}-IFOs, one redundant (null stream), $L=10\,$km
  \onslide<2->
  {
    \begin{footnotesize}
    \begin{align*}
      &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \quad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\quad (\sin 60^\circ =\sqrt{3}/2)\\
      & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
      & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
      %&  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
      \end{align*}
      \end{footnotesize}
    }
   %
    \begin{tikzpicture}[overlay,remember picture]
    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
    \end{tikzpicture}\\
    %
   \onslide<3->
   {
      No blind spots!
      \begin{footnotesize}
      \begin{align*}
      F^2_\bigtriangleup &\equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 \hspace{8cm}\\ 
      &= \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right)
      \end{align*}
      \end{footnotesize}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]

@@

\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
  \vspace{-5mm}
  \begin{footnotesize} 
  \[
  \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  \]
  \\
  \end{footnotesize}
  $\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
  \\
  \onslide<2->
  {
    \vspace{3mm}
    Recall, $\tilde{h}(f) \propto f^{-7/6}$ so $\tilde{h}(f) \sqrt{f} \propto \red{f^{-2/3}}$
    \begin{footnotesize} 
    \[
    \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
    \]
    \end{footnotesize}
  }
  %
  \onslide<3->
  RMS \red{average} over the angles 
  \begin{small}
  $ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
  \end{small}
  \begin{footnotesize} 
  \[
  \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
  \]
  \end{footnotesize}
  %
  Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
  \begin{footnotesize} 
  \[
  0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
  \]
  \end{footnotesize}
  % 
\end{frame}

\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
%
  \begin{footnotesize} 
  \begin{align*}
  \rho_{\text{tot},\red{\llcorner}} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
  \rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
  \end{align*}
  \end{footnotesize}
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
  \end{tikzpicture}
  \\
  %\vspace{2mm}
  \onslide<2->
  {
    $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
    \begin{footnotesize} 
    \[
    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
    \]
    \end{footnotesize}
    \\
  }
  \onslide<3->
  Use \bl{RMS-averaged} $|Q|^2$
  \begin{footnotesize}
  \begin{align*}
  \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
  &=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
  \end{align*}
  \end{footnotesize}
  \\
  %where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
  \vspace{-5mm}
  Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
  \vspace{10mm}
  %
  %
  \begin{tikzpicture}[overlay,remember picture]
  \node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
  \end{tikzpicture}
  %
  % 
\end{frame}

@@

\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
\vspace{-7mm}
  \begin{footnotesize}
    \begin{align*}
      &\tau_\text{insp}^{0\text{PN}}  \simeq 56.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2687 \hspace{2cm} (M=2.73 M_\odot) \\
      &\tau_\text{insp}^{2\text{PN}} \simeq 57.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{2\text{PN}} \simeq 2735 \hspace{2cm} (f_\text{ISCO}\simeq 1611\,\text{Hz}) 
    \end{align*}
  \end{footnotesize}
  \onslide<2->
  {
  What about the SNR? \quad
  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
  \end{small}
  }
  %

%
\begin{tikzpicture}[overlay,remember picture]
    \onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
    {\begin{footnotesize} 
      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
    \end{footnotesize}}; 
    \onslide<2->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(4.1cm,0.1cm)}]current page.center) 
    {\begin{footnotesize} 
      $ \tilde{A}_{i=h,m,l}=A\left\{\tfrac{4}{5},  \tfrac{2}{5},   < \tfrac{1}{5}\right\}$    
    \end{footnotesize}};  
    \onslide<3->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.2cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_{i} = \left\{28.7, \ 14.3, \ 6.00 \right\}$    
    \end{footnotesize}}; 
    \onslide<4->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-2.6cm)}]current page.center) 
    {\begin{footnotesize} 
      $\bar\rho_\text{LHV} = \{ 26.4, 18.8 , 2.0\} $    
    \end{footnotesize}};
    \onslide<3->\node (t5 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
    {\begin{footnotesize} 
      $\rho_\text{tot} = 32.0 $    
    \end{footnotesize}};
        \onslide<4->\node (t6 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-3.1cm)}]current page.center) 
    {\begin{footnotesize} 
      $\rho_\text{tot} = 32.4 $    
    \end{footnotesize}};
    \onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}{The era of Einstein Telescope}{BNS detections}
 Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$\\
 \vspace{1mm}
 \red{Two} ET configurations:\qquad \textcolor{brown}{B} (high $f$), \red{C} (low $f$)
 \begin{tikzpicture}[overlay,remember picture]
      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted_pres.pdf}};
      \onslide<2->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_B_SNR_int.pdf}};
      \onslide<3->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_C_SNR_int.pdf}};
\end{tikzpicture}      
\end{frame}

\begin{frame}{The era of Einstein Telescope}{GRB \red{Forecast} Prospects } 
  \vspace{-8mm}
  \begin{footnotesize}
  \begin{table}[h]
  \centering
  \begin{tabular}{lccccccc}
  %toprule
  \hline\hline
  $D\,$(Mpc) & $R_\text{av}{}^\text{max}_\text{min} $ &  \multicolumn{3}{c}{ET-B}  & \multicolumn{3}{c}{ET-C}\T\B\\
  \hline
  {}& {} & $\bar{f}_\text{ET}\,$(Hz) & \hspace{2mm} $T_\text{AW}$ \hspace{2mm} & $\bar{\rho}_{F}$  & $\bar{f}_\text{ET}\,$(Hz) & \hspace{2mm} $T_\text{AW}\hspace{2mm}$& $\bar{\rho}_{F}$\T\B\\
  %midrule
  100 & $ 1.54^{4.7}_{0.3}$ & $\approx\,$6.72 &  47.0\,minutes & 306  & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
  200 &  $ 12.3^{38}_{2.6} $ & $\approx\,$11.2 & 11.6\,minutes & 152  & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
  400 &$ 98.6^{300}_{20} $ & $\approx\,$18.2 & 3.00\,minutes & 75.7  & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
  600 & $ 333^{1020}_{69} $ & $\approx\,$26.0  &65.8\,seconds & 50.2 &    $\approx\,$5.7 & 1.03\,hours & 60.0  \\
  \hline\hline
  %bottomrule
  \end{tabular}
  \caption*{Event rates using $R=1540^{+3200}_{-1220}\,\text{Gpc}^{-3}\,\text{yr}^{-1}$ inferred from GW170817}
  \end{table}
  \end{footnotesize}
  %
  \vspace{-3mm}
  \onslide<2->Very \red{high SNRs} $\Rightarrow \ord(\rho_F^{\red{-1}})$-precision parameter estimation afterward \\
  \vspace{2mm}
  \onslide<3->\bl{ET-B} $\Longrightarrow $ forecasts not likely \\
  \vspace{2mm}
  \onslide<4->\red{ET-C} $\Longrightarrow T_\text{AW} \ge 1\,$hour within 600\,Mpc\\
  \vspace{1mm}
  \textcolor{white}{ET-C} $\Longrightarrow \red{\ord(100)}$ {\bf BNS forecasts} yearly! $\Rightarrow $ 1 per day!\\
  \vspace{1mm}
  \onslide<5->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(10)}$ with \red{3\,hours} of warning \\
  \vspace{1mm}
  \onslide<6->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(2)}$ with \red{5\,hours} of warning
  \begin{tikzpicture}[overlay,remember picture]
      \onslide<3>\node[draw, blue,thick,minimum width=1.4cm,minimum height=1.6cm] (b) at (-2.6,5.3){};
      \onslide<4->\node[draw, red,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (3.6,5.3){};
  \end{tikzpicture}
\end{frame}

\begin{frame}{The era of Einstein Telescope}{Source localization before the merger} 
  ET is very sensitive, but all 3 IFOs are at one place. \\
  \vspace{1mm}
  $\Longrightarrow$ \red{poor} sky localization \\
  \vspace{1mm}
  \onslide<2->BUT \ldots \\
  \begin{itemize}
  \item With $T_\text{AW} \sim\,$hours, Earth's rotation matters!
  \item Two hours $\Rightarrow 30^\circ \Rightarrow \approx 2000\,$km of IFO distance $\sim\,$L1-H1 separation
  \end{itemize}
  \onslide<3->So, within 1\,Gpc, ET {\bf alone} will localize
  \begin{itemize}
  \item 20\% of the sources to within 100\,deg$^2$
  \item 2\% to within 20\,deg$^2$
  \item 0.5\% to within 10\,deg$^2$ 
  \onslide<4->\item[]$\Longrightarrow \red{5}$ to \red{10} sources within 400\,Mpc
  \end{itemize}
  \onslide<5->10\,deg$^2$: LSST's field of view\\
  \onslide<6-> Numbers improve with \bl{Cosmic Explorer} ($f\gtrsim \red{5}\,$Hz)
  %
  \begin{tikzpicture}[overlay,remember picture]
	\onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.2cm,2.25cm)}]current page.center) {\includegraphics[height=3cm]{figs/Earth_rot.png}};
	\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.3cm,-2.25cm)}]current page.center) {\includegraphics[height=3.9cm]{figs/LSST.jpg}};
  \end{tikzpicture}
\end{frame}
